Modeling defoliation as a proxy for tree health: A case study using machine-learning and hyperspectral remote sensing data

### 2019-06-16 code/98-paper/journal/manuscript.tex
Updates from Overleaf

>>>>

Most other studies analyzing defoliation operated on the plot rather than the tree level due to spatial resolution of the satellite products that served as the input data (\citep{townsend2012, debeurs2008a}.
Studies focusing on the tree-level used ground-level methods such as \ac{ALS} or \ac{LiDAR} \citep{meng2018, kalin2019}.
